### 2024-01-25 manuscript.tex
Update manuscript.tex
referred to a format in the YouTube version: ms.jansub.tex

\documentclass[12pt,]{article}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{adjustbox}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage{longtable}
\usepackage{url,hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

\usepackage{longtable,booktabs}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\newcommand{\comment}[1]{\textbf{[[#1]]}}
\newcommand{\cfcmt}[1]{\comment{CFS: #1}}
\newcommand{\cfonly}[1]{\comment{CFS (note): #1}}
\newcommand{\cf}[1]{\comment{CFS (comment or note?): #1}}
\newcommand{\jdcmt}[1]{\comment{JD: #1}}
\newcommand{\mlcmt}[1]{\comment{MLi: #1}}

\bibliographystyle{plain}

\date{}

@@

\subsection{Manuscript}\label{manuscript}

\subsubsection{Title}\label{title}

Female Genital Cutting Is a Social Coordination Norm in Kenya, Mali, Nigeria and Sierra Leon
\cfcmt{This title is a response to Efferson’s title}

\subsubsection{Authors}\label{authors}

Chyun-Fung Shi (corresponding author), Department of Biology, McMaster
University. Michael Li, Department of Biology, McMaster University.
Jonathan Dushoff, Department of Biology, McMaster
University.

\subsection{journals}\label{journals}
possible consideration:  The Lancet Global Health, Science, BMJ, Bulletin of WHO

\subsection{Abstract}\label{abstract}

\subsubsection{Context}\label{context}

\subsubsection{}\label{objective}

\subsubsection{Methods}\label{Methods}

\subsubsection{Main Outcome Measures}\label{main-outcome-measures}

\subsubsection{Results}\label{results}

\subsubsection{Conclusions}\label{conclusions}

\subsubsection{Funding}\label{funding}

\subsubsection{Keywords}\label{keywords}

female genital cutting/mutilation, multilevel model, social norms, gender, DHS

\subsection{Introduction}\label{introduction}

Female genital cutting (FGC), circumcision or mutilation is a form of female's genital mutilation \cfonly{cite}, Following Tostan \cite{Tost15} \cfonly{update to make sure Tostan still perfers the term}, we used cutting instead of circumcision in this study without excusing the negative impact of the practice while recognizing a sense of self-awareness in making decision about FGC \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}. \cfonly{less cites and update cites}.  It is estimated that more than xxx million women and girls will have undergone female genital cutting (FGC), mostly in Africa and the Middle East, between 20xx to 20xx; and among them, xx million are girls below age 15 \cfonly{based on a UNICEF global database \cite{AdnrLesc16, UNIC16} \cfcmt{check cites and adding KandEzej18? update}. The prevalence might be underreported due to a deeply embedded cultural practice that is mostly illegal \cite{StevKell22}.  FGC is embodied with multiple approaches from cultural and religious identity in one end, and public health and human rights concerns on the other \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, McCh15, SchuLien13, WHO12} \cfonly{too many cites and update}.  The commonly international position of FGC is about abolishment than intervention of the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}\cfonly{update}.  Progress of intervention is impeded because of the complicated FGC history \cite{BergDeni12, Cami16} and of not keeping up with the population growth \cite{KhosBane17, UNIC16}.

Knowledge and attitudes in supporting FGC abolishment did not necessarily translate to abandon the practice nor the intention not to modify women's genitals \cite{ChegAske04, Bicc10, Cami15, CislHeis18, Mack96} \cfonly{more cites}.  Understanding reasons and values attached to FGC is essential for comprehending the persistence of the practice \cite{Bicc10, Cami15, CislHeis18, Mack96, Youn15} \cfonly{update}.  There is a considerable interest in applying social norm, a form of values driving behavioural patterns which are self-enforcing within a group \cite{Youn15}, to the intervention of public health behaviours \cite{Ajze91, Ajze02, CislHeis18a, MillPrin16, MollRima10, RimaLapi15} \cfonly{focus on FGC instead of the health behaviours in general, and update cites}.  FGC norms are deeply internalized and morally embraced \cite{SchuLien13} \cfonly{update}.  Social convention theory, a leading theory probing FGC tradition (e.g., see \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12} \cfonly{update}) initially proposed that FGC was a marriageability convention through coordination \cite{Mack96} and extended to broader social norms, such as social prestige, adolescent rite of passage, and female honour and modesty \cite{Mack00, MackLeJe08} \cfonly{more cites}.   The social convention theory regards FGC a social behaviour interdependent among and coordinated by members in their social network \cite{Mack00, MackLeJe08, ShelWand11} \cfonly{more cites}.  As no coordination game was observed in marital expectation in community with FGC tradition \cite{EffeVogt15}\cfonly{more cites}, studies showed that factors other than marriageability, such as \cfonly{examples}, have underlined women’s  decisions of FGC \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}.  FGC was also viewed as a form of social capital, a value respected by women for inclusion within their social groups \cite{ShelWand11}.   The practice was strongly correlated with social expectation (i.e., what other people do or what other people believe one should do)\cite{BiccMari15} \cfonly{more cites}.   Basically, when FGC norms within the communities are strong, individuals tend to self-enforce and coordinate such norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} \cfonly{add \cite{Bicc15}}\cfonly{more cites}.

Understanding social norms of FGC provides a venue in negotiating sustainable changes of the practice \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less and update}.  In this study, we anlayzed types of social values of FGC perceived in communities and the associations of social values and FGC practice.  Although FGC norms were studied as aforementioned, there was limited analysis of how individual normative attitudes (e.g., attitudinal position of FGC values) and behavioural intention intertwining with the group norm.  Such information is expected to extend understandings of the persistence of FGC practice.  We believe this is the first FGC study using modules of FGC normative attitudes to model the FGC intention by utilizing the norm in the context of community influence.

\subsection{Research Questions}\label{research-questions}

There are two research questions:  what is the association of daughter's FGC future and mothers' FGC beliefs, and what is the association of FGC continuance and FGC beliefs. The research presumption was based on the studies aforementioned that women’s FGC intention on their daughters was dependent on other women’s attitudes on this practice \cfonly{descriptive norms?!}.  Attitude is a personal evaluation of behaviour \cite{Ajze91}, a sensible proxy of social norm \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11}\cfonly{cut cites}}.  It is an important index used to evaluate fgc practices \cite{CislHeis18, EffeVogt15, Harf06, ModrLiu13, PashPonn16, ShelHern06,}} \cfonly{check cites}.  However, there was little quantitative research on the relationship between attitudes and intention of circumcising daughters at both an individual and community level while taking beliefs of FGC benefits into account.

Two main models were constructed in response to the two research questions mentioned above:  the daughter model, and the continuance model.  In addition, we also tested a “persistence” model, to examine the association of FGC benefits and FGC continuance on mothers' intention on FGC their  daughters.  Both of the continuance model and the persistence model were purposed to further understand how the position of the main model could be changed under the two structural models.

\subsection{Methods}\label{methods}

\subsubsection{Data}\label{data}

We analyzed the secondary data of women aged 15-49 from the Demographic and Health Surveys (DHS) when it met the research criteria:  countries with high FGC prevalence \cite{UNIC16}, and with the modules of FGC status, FGC benefit, and gender awareness. As a result, four countries of the most recent datasets were selected: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008 \cfcmt{checked and updated in Nov 6, 2023.}   Although the datasets seemed outdated, it should not affect the study object to understand FGC norms and behaviors.  \cfcmt{See https://github.com/fishforwish/fgc/blob/master/README.md for updated info}.

@@

\subsubsection{Measurements}\label{measurements}

\cfonly{\cite{Rima08}}*

The main responses and predictors in the models are as: FGC benefits (predictor) -->  to FGC daughters (response) in the daughter model, FGC benefits --> FGC future in the continuance model, and FGC benefits and FGC continuance --> to FGC daughters in the persistence model.  The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of FGC beliefs associating with FGC practice.

The co-variables were basic social demographic factors (i.e., country, education, job, residence (rural vs. urban), religion, marital status, age, media use, and wealth) in addition to gender awareness.  Gender awareness (see — for questions of gender awareness proxy) was included to test if women’s gender awareness interacted with their intention of FGC daughters and their position of FGC practice overall \cfonly{cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} check and cut}.  Media use and gender awareness were also scored.  Cluster ID (i.e., villages where the samples were from) and ethnicity (see the list of ethnicity recode at table xx in appendix) \cfonly{with a footnote on how we recoded it} were treated as random variables.  Ethnicity was treated as a random effect based on previous study which showed little differences in results using individual rather than cluster ethnicity \cite{Hayf05}.

Regarding potential community impact on the practice of FGC, the following factors were also tested at a community level:  mothers' intention on FGC daughters, FGC continuance, and FGC benefits as well as the basic social-demographic factors:  education, wealth, media use, gender awareness and FGC prevalence \cfcmt{to confirm:  it's on a cluster level, not national.  Correct?} with cluster as a proxy to represent a community level of impact \cite{AligRen06, BoylSvec19, Hayf05, Krav02}.

\cfcmt{Regarding FGC benefits modules, there were 9 questions.  Kenya had all the 9, Mali and SL 7 missing promiscuity and STD, NG 8 missing STD).  Should we drop STD since 3 out of 4 missed this variable?}
\jdcmt{Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.} \cfcmt{Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.  But as J said, it is too hard! } \cfcmt{Whatever we decide, we need a reason in this section to justify our decision. After all, ethnicity is better to be a fixed factor but we can’t because it breaks down the models!}

\cfcmt{“explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior” \cite{Hayf05}}
\cfcmt{Bayesian model \cite{KandNwak09} “Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level. Consequently, the spatial analysis will be affected by some random fluctuations.  Some of this random variation can be reduced through structured spatial effects because it includes neighboring observations in the analysis. However, it should be pointed out that such a spatial analysis should preferably be applied to census data, where the precision of the spatial analysis would be much higher." (p. 788)}

\cfonly {in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).

\subsubsection{Statistical Model}\label{statistical-model}

We used cumulative link mixed models (CLMMs) in the statistics package R \cite{Rstats,Rpackage_ordinal} to analyze the models.  The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of applying FGC to daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.  
We subtracted respondent (-1) from the cluster when testing the community effect \cfcmt{Please rewrite this. Also, do we need to mention how we treat cluster with only one sample (if that happens).}
\cfcmt{Please explain why we didn’t do sampling weight.}
\cfcmt{Do we explain conveyance of uncertainty}

@@

\cfcmt{Do we do any within-community variation and between-community variation?  Is it a thing?
}

\cfonly{reference: Methods and the first paragraph of Discussion\cite{Chia14}}

\subsubsection{Scripts}\label{scripts}

@@

\subsection{Results}\label{results-1}

@@

\cfcmt{M: sample size of daughters plan in sociodemographic figure?  It should be only the women with daughters for fgc.}

The results of the three models are at figure xxx \cf{isoplots and effect plots}.  The findings showed robust results.  The main predictors, women’s fgc status, beliefs of fgc benefits and FGC prevalence were all clearly and positively associated with the two responses (intention to cut daughters and attitudes on whether FGC should be continued) in all the three models; so as the following factors but in negative associations:  age, education, media, religion and the community levels of beliefs of FGC benefits \cf{this one is tricky to interpret}.  In addition, group level of intention to cut daughters was also clearly and positively associated with respondents’ intention to cut their daughter, as well as group persistence of FGC practice with the women’s attitudes on FGC practice.   Although gender awareness was positively associated with both responses but only at an individual level not a group level.

Basically, After adjusting for individual- and community-level factors, our main models indicated that respondents’ intention of having their daughters cut was mostly associated with the group intention on this matter (see Fig x daughterPlan-effects-plot.Rout.pdf and iso plots) \cf{group-daughterPlan  142.11  1  < 2.2e-16.  How to transfer this into a more understandable sentence?}:  the stronger the intention of cutting daughters within their group, the more likely a respondent’s intention to cut their daughters.  Similarly in the persistent model (see persistence effect plots and iso plots), the higher the attitudes on carrying on FGC practice within a group, the more likely a respondent’s attitude on supporting such a practice.  Both models also showed that women’s beliefs in FGC benefits and their FGC status positively related to their likelihood of cutting their daughters, and supporting the practice.

@@

\cf{Need some discuss of the mixed model:  how it help to clarify our main models or what?}
\cf{in daughter model, gender awareness (P<0.05) should be below group gender awareness (P>0.05) on effect plots based on the valvisum.Rout.  So is there a mistake? }
\cfcmt{Why isn’t mixed model our main model?}
\cfcmt{M: individual persistence is missing in the mixed model}

Tables and figures to be included:
\cf{We need to show both isoplots and effect plots because some binary variables are not on the isoplots.}
- a figure of women’s FGC prevalence vs. their intention of cutting daughters vs. attitudes towards FGC continuity.  (ref to \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/}, Fig 1)
- figure:  plots of FGC benefits (This figure will be important. It tells us what women thinks about why FGC).
- figure: to put the first PCA of FGC believes of the 4 nations at the community level and maybe in one figure
- prevalence.Rout.pdf
% a chart like figure 8-8D \cite{UNIC13}

\subsection{Discussion}\label{Discussion}

@@

Our models showed that the four countries were clearly different in intention of cutting their daughters with Sierra Lion of the highest likelihood and Nigeria compared to FGC prevalence where Sierra Leon had the highest prevalence, followed by Mali, Nigeria and Kenya; yet their attitudes of supporting FGC practice was not clear despite the factor of FGC prevalence \cf{figure xx and figure xxx}.  Regarding sociodemographic factors, education (community), wealth (individual and community) and job (individual) did not predict women’s intention on cutting their daughters, nor did gender awareness (community).

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\author{}
\date{}

@@

Female Genital Cutting Is a Social Coordination Norm in Kenya, Mali, Nigeria and Sierra Leon

Chyun-Fung Shi (1), Mike Li (2,3), Jonathan Dushoff (1,2,4)

1 Department of Biology, McMaster University, Hamilton, ON, Canada.
2 Department of Mathematics and Statistics, McMaster University, Hamilton, ON, Canada.
3 PHAC, ON, Canada.
4 Michael G. DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, ON, Canada.

\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

\textbf{Objective:}  
\textbf{Methods:} 
\textbf{Results:} 
\textbf{Conclusion:} 
\textbf{Objective:}

\hypertarget{keywords}{%
\section{Keywords}\label{keywords}}

Female genital cutting, female circumcision, social norm, health behavior.

\hypertarget{background}{%
\section{Background}\label{background}}

Female genital cutting (FGC), circumcision or mutilation is a form of altering or injuring female's genitalia for non-medical reasons. [UNIC21], Following Tostan [Tost15], we used cutting instead of circumcision or mutilation in this study without excusing the negative impact of the practice while recognizing a sense of self-awareness in making decision about FGC [JohnEsse10, Meye00, Shel01, Tost15]. \cfonly{less cites and update cites].  It is estimated that more than xxx million women and girls will have undergone female genital cutting (FGC), mostly in Africa and the Middle East, between 20xx to 20xx; and among them, xx million are girls below age 15 \cfonly{based on a UNICEF global database} [AdnrLesc16, UNIC16] \cfcmt{check cites and adding KandEzej18? update}. The prevalence might be underreported due to a deeply embedded cultural practice that is mostly illegal [StevKell22].  FGC is embodied with multiple approaches from cultural and religious identity in one end, and public health and human rights concerns on the other [AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, McCh15, SchuLien13, WHO12] \cfonly{too many cites and update}.  The commonly international position of FGC is about abolishment than intervention of the practice [KhosBane17, Mack96, Toub94, UNIC16, WHO97]\cfonly{update}.  Progress of intervention is impeded because of the complicated FGC history [BergDeni12, Cami16] and of not keeping up with the population growth [KhosBane17, UNIC16].

Knowledge and attitudes in supporting FGC abolishment did not necessarily translate to abandon the practice nor the intention not to modify women's genitals [ChegAske04, Bicc10, Cami15, CislHeis18, Mack96] \cfonly{more cites}.  Understanding reasons and values attached to FGC is essential for comprehending the persistence of the practice [Bicc10, Cami15, CislHeis18, Mack96, Youn15] \cfonly{update}.  There is a considerable interest in applying social norm, a form of values driving behavioural patterns which are self-enforcing within a group [Youn15], to the intervention of public health behaviours [Ajze91, Ajze02, CislHeis18a, MillPrin16, MollRima10, RimaLapi15] \cfonly{focus on FGC instead of the health behaviours in general, and update cites}.  FGC norms are deeply internalized and morally embraced [SchuLien13] \cfonly{update}.  Social convention theory, a leading theory probing FGC tradition (e.g., see [BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12] \cfonly{update}) initially proposed that FGC was a marriageability convention through coordination [Mack96] and extended to broader social norms, such as social prestige, adolescent rite of passage, and female honour and modesty [Mack00, MackLeJe08] \cfonly{more cites}.

The social convention theory regards FGC a social behaviour interdependent among and coordinated by members in their social network [Mack00, MackLeJe08, ShelWand11] \cfonly{more cites}.  As no coordination game was observed in marital expectation in community with FGC tradition [EffeVogt15]\cfonly{more cites}, studies showed that factors other than marriageability, such as \cfonly{examples}, have underlined women’s  decisions of FGC [AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?].  FGC was also viewed as a form of social capital, a value respected by women for inclusion within their social groups [ShelWand11].   The practice was strongly correlated with social expectation (i.e., what other people do or what other people believe one should do)[BiccMari15] \cfonly{more cites}.   Basically, when FGC norms within the communities are strong, individuals tend to self-enforce and coordinate such norms [Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92] \cfonly{add [Bicc15]]\cfonly{more cites}.

Understanding social norms of FGC provides insights of the gaps between both camps on each end mentioned above, and a venue in negotiating sustainable changes of the practice [Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13] \cfonly{less and update}.  In this study, we analyzed types of social norms of FGC perceived in communities and the associations of the FGC norms and the practice.  Although there have been studies on FGC norms as aforementioned, there was limited calcification of types of individual normative attitudes (e.g., attitudinal position of FGC values) and behavioural intention in response to the community norm.  Such information is expected to extend understandings of the persistence of FGC practice.  We believe this is the first FGC study using modules of FGC normative attitudes to model the FGC intention by utilizing the norm in the context of community influence.

Research Questions
=================
\hypertarget{Research-Questions}{%
\section{Research Questions}\label{Research-Questions}}

There are two research questions:  what is the association of daughter's FGC future and mothers' FGC beliefs, and what is the association of FGC continuance and FGC beliefs. The research presumption was based on the studies aforementioned that women’s FGC intention on their daughters was dependent on other women’s attitudes on this practice \cfonly{descriptive norms?!}.  Attitude is a personal evaluation of behaviour [Ajze91], a sensible proxy of social norm \cfonly {norm theory [Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11]\cfonly{cut cites}].  It is an important index used to evaluate fgc practices [CislHeis18, EffeVogt15, Harf06, ModrLiu13, PashPonn16, ShelHern06,]} \cfonly{check cites}.  However, there was little quantitative research on the relationship between attitudes and intention of circumcising daughters at both an individual and community level while taking beliefs of FGC benefits into account.

Two main models were constructed in response to the two research questions mentioned above:  the daughter model, and the continuance model.  In addition, we also tested a “persistence” model, to examine the association of mothers' intention on FGC their daughters and their view of FGC continuance FGC benefits predicted by mother's FGC status and their FGC beliefs .  The persistence model was purposed to further understand how the position of the main model could be changed under mother's attitude on FGC continuance.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{data-selection}{%
\subsection{Data selection}\label{data-selection}}

We analyzed the secondary data of women aged 15-49 from the Demographic and Health Surveys (DHS) when it met the research criteria:  countries with high FGC prevalence [UNIC16], and with the modules of FGC status, FGC benefit, and gender awareness. As a result, four countries of the most recent datasets were selected: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008 \cfcmt{checked and updated in Nov 6, 2023.}   Although the datasets seemed outdated, it should not affect the study object to understand FGC norms and behaviors.  \cfcmt{See https://github.com/fishforwish/fgc/blob/master/README.md for updated info}.

@@

\hypertarget{Measurements}{%
\subsection{Measurements}\label{Measurements}}

\cfonly{[Rima08]]}*

The main responses and predictors in the models are as: FGC benefits (predictor) -->  to FGC daughters (response) in the daughter model, FGC benefits --> FGC future in the continuance model, and FGC benefits and FGC continuance --> to FGC daughters in the persistence model.  The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm] to identify the strength of FGC beliefs associating with FGC practice.

The co-variables were basic social demographic factors (i.e., country, education, job, residence (rural vs. urban), religion, marital status, age, media use, and wealth) in addition to gender awareness.  Gender awareness (see — for questions of gender awareness proxy) was included to test if women’s gender awareness interacted with their intention of FGC daughters and their position of FGC practice overall \cfonly{cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02] check and cut].  Media use and gender awareness were also scored.  Cluster ID (i.e., villages where the samples were from) and ethnicity (see the list of ethnicity recode at table xx in appendix) \cfonly{with a footnote on how we recoded it] were treated as random variables.  Ethnicity was treated as a random effect based on previous study which showed little differences in results using individual rather than cluster ethnicity [Hayf05].

Regarding potential community impact on the practice of FGC, the following factors were also tested at a community level:  mothers' intention on FGC daughters, FGC continuance, and FGC benefits as well as the basic social-demographic factors:  education, wealth, media use, gender awareness and FGC prevalence \cfcmt{to confirm:  it's on a cluster level, not national.  Correct?] with cluster as a proxy to represent a community level of impact [AligRen06, BoylSvec19, Hayf05, Krav02].

\cfcmt{Regarding FGC benefits modules, there were 9 questions.  Kenya had all the 9, Mali and SL 7 missing promiscuity and STD, NG 8 missing STD).  Should we drop STD since 3 out of 4 missed this variable?]
\jdcmt{Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.] \cfcmt{Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.  But as J said, it is too hard! ] \cfcmt{Whatever we decide, we need a reason in this section to justify our decision. After all, ethnicity is better to be a fixed factor but we can’t because it breaks down the models!]

\cfcmt{“explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior” [Hayf05]]
\cfcmt{Bayesian model [KandNwak09] “Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level. Consequently, the spatial analysis will be affected by some random fluctuations.  Some of this random variation can be reduced through structured spatial effects because it includes neighboring observations in the analysis. However, it should be pointed out that such a spatial analysis should preferably be applied to census data, where the precision of the spatial analysis would be much higher." (p. 788)]

\cfonly {in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see [Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02])}

\hypertarget{Statistical-Model}{%
\subsection{Statistical Model}\label{Statistical-Model}}

We used cumulative link mixed models (CLMMs) in the statistics package R [Rstats,Rpackage_ordinal] to analyze the models.  The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of applying FGC to daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.  
We subtracted respondent (-1) from the cluster when testing the community effect \cfcmt{Please rewrite this. Also, do we need to mention how we treat cluster with only one sample (if that happens).}
\cfcmt{Please explain why we didn’t do sampling weight.}
\cfcmt{Do we explain conveyance of uncertainty}

@@

\cfcmt{Do we do any within-community variation and between-community variation?  Is it a thing?

}

\cfonly{reference: Methods and the first paragraph of Discussion[Chia14]}

\hypertarget{Scripts}{%
\subsection{Scripts}\label{Scripts}}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

@@

\cfcmt{M: sample size of daughters plan in sociodemographic figure?  It should be only the women with daughters for fgc.]

The results of the three models are at figure xxx \cf{isoplots and effect plots].  The findings showed robust results.  The main predictors, women’s fgc status, beliefs of fgc benefits and FGC prevalence were all clearly and positively associated with the two responses (intention to cut daughters and attitudes on whether FGC should be continued) in all the three models; so as the following factors but in negative associations:  age, education, media, religion and the community levels of beliefs of FGC benefits \cf{this one is tricky to interpret].  In addition, group level of intention to cut daughters was also clearly and positively associated with respondents’ intention to cut their daughter, as well as group persistence of FGC practice with the women’s attitudes on FGC practice.   Although gender awareness was positively associated with both responses but only at an individual level not a group level.

Basically, After adjusting for individual- and community-level factors, our main models indicated that respondents’ intention of having their daughters cut was mostly associated with the group intention on this matter (see Fig x daughterPlan-effects-plot.Rout.pdf and iso plots) \cf{group-daughterPlan  142.11  1  < 2.2e-16.  How to transfer this into a more understandable sentence?]:  the stronger the intention of cutting daughters within their group, the more likely a respondent’s intention to cut their daughters.  Similarly in the persistent model (see persistence effect plots and iso plots), the higher the attitudes on carrying on FGC practice within a group, the more likely a respondent’s attitude on supporting such a practice.  Both models also showed that women’s beliefs in FGC benefits and their FGC status positively related to their likelihood of cutting their daughters, and supporting the practice.

@@

\cf{Need some discuss of the mixed model:  how it help to clarify our main models or what?]
\cf{in daughter model, gender awareness (P<0.05) should be below group gender awareness (P>0.05) on effect plots based on the valvisum.Rout.  So is there a mistake? ]
\cfcmt{Why isn’t mixed model our main model?]
\cfcmt{M: individual persistence is missing in the mixed model]

Tables and figures to be included:
\cf{We need to show both isoplots and effect plots because some binary variables are not on the isoplots.]
- a figure of women’s FGC prevalence vs. their intention of cutting daughters vs. attitudes towards FGC continuity.  (ref to \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/], Fig 1)
- figure:  plots of FGC benefits (This figure will be important. It tells us what women thinks about why FGC).
- figure: to put the first PCA of FGC believes of the 4 nations at the community level and maybe in one figure
- prevalence.Rout.pdf
% a chart like figure 8-8D [UNIC13]

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

Our models showed that the four countries were clearly different in intention of cutting their daughters with Sierra Lion of the highest likelihood and Nigeria compared to FGC prevalence where Sierra Leon had the highest prevalence, followed by Mali, Nigeria and Kenya; yet their attitudes of supporting FGC practice was not clear despite the factor of FGC prevalence \cf{figure xx and figure xxx].  Regarding sociodemographic factors, education (community), wealth (individual and community) and job (individual) did not predict women’s intention on cutting their daughters, nor did gender awareness (community).

The positive impact modernization [BoylMcMo02, Youn02] and gender/feminist perspectives [BoylSvec19, DalaLawo10, Dell04, FrieMahm13, KandNwak09, Lewi04, Meye00, Njam04, YirgKass12, Youn02] on intention of cutting daughters were not obvious than the convention approach in our findings as well as previously concluded [Hayf05] \cfonly{to confirm]. While a daughter’s FGC risk was higher if she was in a community with a higher community-level of women’s extra familial opportunities (e.g., education, paid work and marital background) [GrosHayf19], our findings showed that community level of education was not a clear determinant of daughter’s FGC risk, compare to a previous study showed that community education had no clear effect on the likelihood of daughter’s FGC future, while the individual education did in Kenya [Hayf05].
